### 2019-10-23 figures/07_model-selection.Rmd
better planel spacing

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)

>>>>

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)

### 2019-10-23 tables/02_cdl_key.Rmd

\pagebreak
```{r cdl_summary}
# ---- cdl summary ----
cdl_data <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)

apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
                                        na.rm = TRUE)) %>%
  data.frame() %>%
  dplyr::select(-llid) %>%
  t() %>%
  knitr::kable(caption = "CDL summary statistics", format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%
  add_header_above(c(" ", "Quantiles" = 3))
```

>>>>

\pagebreak
```{r cdl_summary}
# setwd("tables")
# ---- cdl summary ----
cdl_data <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)

dt <- apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
                                        na.rm = TRUE)) %>%
  data.frame() %>%
  dplyr::select(-llid)

dt %>%
  t() %>%
  knitr::kable(caption = "CDL summary statistics", digits = 2,
               format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%
  add_header_above(c(" ", "Quantiles" = 3))
```
